NGO analysis

### 2022-07-26 Dashboard/NGO Analysis dashboard alpha.Rmd
OrOr? AndAnd. (Programming logicals).

  ## CEO compensation-----------------------------------------------------------
  CEO_plot <- reactive({
    # Testing for the presence of data
    if (sum(!is.na(htmldata()$lederlonn)) == 0 &
      sum(!is.na(htmldata()$leder_annen_godtgjorelse)) == 0) {
      # Printing 'no information' plot if no data
      no_information()
    } else {
      # Creating plot if any data exist
      # Note that the plot will still look empty, but have a legend and scales,
      # if all values are explicit zeroes
      htmldata() |>
        # preparing for pivoting
        select(
          year, lederlonn, leder_annen_godtgjorelse
        ) |>
        # Compensation in ordinary numbers
        mutate(
          lederlonn = lederlonn * 1000,
          leder_annen_godtgjorelse = leder_annen_godtgjorelse * 1000
        ) |>
        # renaming for the purposes of the plot
        rename(
          Year = year,
          Salary = lederlonn,
          `Other compensation` = leder_annen_godtgjorelse
        ) |>
        # pivoting to join the two values to use fill
        pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |>
        ggplot(aes(Year, value, fill = Compensation)) +
        geom_col() +
        # using currency scale function to add correct currency code or ?
        currency_scale() +
        # pretty colours
        scale_fill_met_d("Hokusai2", direction = -1) +
        labs(
          x = "", y = "Total compensation", title = "CEO compensation"
        )
    }
  })

>>>>

  ## CEO compensation-----------------------------------------------------------
  CEO_plot <- reactive({
    # Testing for the presence of data
    if (sum(!is.na(htmldata()$lederlonn)) == 0 &&
      sum(!is.na(htmldata()$leder_annen_godtgjorelse)) == 0) {
      # Printing 'no information' plot if no data
      no_information()
    } else {
      # Creating plot if any data exist
      # Note that the plot will still look empty, but have a legend and scales,
      # if all values are explicit zeroes
      htmldata() |>
        # preparing for pivoting
        select(
          year, lederlonn, leder_annen_godtgjorelse
        ) |>
        # Compensation in ordinary numbers
        mutate(
          lederlonn = lederlonn * 1000,
          leder_annen_godtgjorelse = leder_annen_godtgjorelse * 1000
        ) |>
        # renaming for the purposes of the plot
        rename(
          Year = year,
          Salary = lederlonn,
          `Other compensation` = leder_annen_godtgjorelse
        ) |>
        # pivoting to join the two values to use fill
        pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |>
        ggplot(aes(Year, value, fill = Compensation)) +
        geom_col() +
        # using currency scale function to add correct currency code or ?
        currency_scale() +
        # pretty colours
        scale_fill_met_d("Hokusai2", direction = -1) +
        labs(
          x = "", y = "Total compensation", title = "CEO compensation"
        )
    }
  })

### 2022-07-26 Dashboard/report.Rmd
OrOr? AndAnd. (Programming logicals).

## Creating the Excel warning text --------------------------------------------
excel_warning <- if (datatest == TRUE) {
  "**    Warning: something is wrong with the Excel data.**"
} else {
  ""
}

@@

# Creating the CEO_plot warning text
CEO_plot_warning <- if (sum(!is.na(htmldata$lederlonn)) == 0 &
    sum(!is.na(htmldata$leder_annen_godtgjorelse)) == 0) {
  "*    No information about CEO compensation is available.*"
} else {
  ""
}

# Creating general warning
general_warning <- if (datatest == TRUE | sum(!is.na(htmldata$arsresultat)) == 0 | sum(!is.na(htmldata$sum_egenkapital_og_gjeld)) == 0 | (sum(!is.na(htmldata$lederlonn)) == 0 &
    sum(!is.na(htmldata$leder_annen_godtgjorelse)) == 0)) {
  "## Note:"
} else {
  ""
}
```

@@

### NA warning-----------------------------------------------------------------
# Testing for the presence of NAs; printing warning if there are any
KPI_warning <- if (is.na(fundraising) | is.na(KPI_OPX) | is.na(KPI_private) |
  is.na(KPI_public) | is.na(KPI_proportion)) {
  "*A value of 'NA' indicates that there is something wrong with the Excel data, that the necessary data are not available, or that the data are unsuited to an automatic calculation of the KPI.*"
} else {
  ""
}
```

@@

```{r compensation_plot, out.width="100%", fig.cap="Based on the category \`Lederlønn' in the Proff.no data. Not in thousands. Includes the entries \`Lønn' and \`Leder annen godtgjørelse'. A common measure of transparency, but should normally be evaluated in context."}
## CEO compensation-----------------------------------------------------------
CEO_plot <-
  # Testing for the presence of data
  if (sum(!is.na(htmldata$lederlonn)) == 0 &
    sum(!is.na(htmldata$leder_annen_godtgjorelse)) == 0) {
    # Returning NA if no data
    NA
  } else {
    # Creating plot if any data exist
    # Note that the plot will still look empty, but have a legend and scales,
    # if all values are explicit zeroes
    htmldata |>
      # preparing for pivoting
      select(
        year, lederlonn, leder_annen_godtgjorelse
      ) |>
      # Compensation in ordinary numbers
      mutate(
        lederlonn = lederlonn * 1000,
        leder_annen_godtgjorelse = leder_annen_godtgjorelse * 1000
      ) |>
      # renaming for the purposes of the plot
      rename(
        Year = year,
        Salary = lederlonn,
        `Other compensation` = leder_annen_godtgjorelse
      ) |>
      # pivoting to join the two values to use fill
      pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |>
      ggplot(aes(Year, value, fill = Compensation)) +
      geom_col() +
      # using currency scale function to add correct currency code or ?
      currency_scale +
      # pretty colours
      scale_fill_met_d("Hokusai2", direction = -1) +
      labs(
        x = "", y = "Total compensation", title = "CEO compensation"
      ) +
      theme(legend.position = "bottom")
  }

>>>>

## Creating the Excel warning text --------------------------------------------
excel_warning <- if (datatest == TRUE) {
  "***    Warning: something is wrong with the Excel data.***"
} else {
  ""
}

@@

# Creating the CEO_plot warning text
CEO_plot_warning <- if (sum(!is.na(htmldata$lederlonn)) == 0 &&
    sum(!is.na(htmldata$leder_annen_godtgjorelse)) == 0) {
  "*    No information about CEO compensation is available.*"
} else {
  ""
}

# Creating general warning
general_warning <- if (datatest == TRUE || sum(!is.na(htmldata$arsresultat)) == 0 || sum(!is.na(htmldata$sum_egenkapital_og_gjeld)) == 0 || (sum(!is.na(htmldata$lederlonn)) == 0 &&
    sum(!is.na(htmldata$leder_annen_godtgjorelse)) == 0)) {
  "## Note:"
} else {
  ""
}
```

@@

### NA warning-----------------------------------------------------------------
# Testing for the presence of NAs; printing warning if there are any
KPI_warning <- if (is.na(fundraising) || is.na(KPI_OPX) || is.na( KPI_private) ||
  is.na(KPI_public) || is.na(KPI_proportion)) {
  "*A value of 'NA' indicates that there is something wrong with the Excel data, that the necessary data are not available, or that the data are unsuited to an automatic calculation of the KPI.*"
} else {
  ""
}
```

@@

```{r compensation_plot, out.width="100%", fig.cap="Based on the category \`Lederlønn' in the Proff.no data. Not in thousands. Includes the entries \`Lønn' and \`Leder annen godtgjørelse'. A common measure of transparency, but should normally be evaluated in context."}
## CEO compensation-----------------------------------------------------------
CEO_plot <-
  # Testing for the presence of data
  if (sum(!is.na(htmldata$lederlonn)) == 0 &&
    sum(!is.na(htmldata$leder_annen_godtgjorelse)) == 0) {
    # Returning NA if no data
    NA
  } else {
    # Creating plot if any data exist
    # Note that the plot will still look empty, but have a legend and scales,
    # if all values are explicit zeroes
    htmldata |>
      # preparing for pivoting
      select(
        year, lederlonn, leder_annen_godtgjorelse
      ) |>
      # Compensation in ordinary numbers
      mutate(
        lederlonn = lederlonn * 1000,
        leder_annen_godtgjorelse = leder_annen_godtgjorelse * 1000
      ) |>
      # renaming for the purposes of the plot
      rename(
        Year = year,
        Salary = lederlonn,
        `Other compensation` = leder_annen_godtgjorelse
      ) |>
      # pivoting to join the two values to use fill
      pivot_longer(c(Salary, `Other compensation`), names_to = "Compensation") |>
      ggplot(aes(Year, value, fill = Compensation)) +
      geom_col() +
      # using currency scale function to add correct currency code or ?
      currency_scale +
      # pretty colours
      scale_fill_met_d("Hokusai2", direction = -1) +
      labs(
        x = "", y = "Total compensation", title = "CEO compensation"
      ) +
      theme(legend.position = "bottom")
  }
